The necessity of hypermedia RDF and an approach to achieve it

### 2012-03-07 eswc-2012/workshop2.tex
grammartypo trim some HTTP qualifications
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@166 43ef1190-90fd-4dd7-a769-d0121f02b80e

Semantic Web services are likely to be an important source of data for
future applications, but for foreseeable future they are just one of many. A
key promise of the Semantic Web is the ability to integrate many data
sources easily. There are two key issues, first read-write operations
must be similar to how it is done with other hypermedia types, to make
it possible to use generic code to minimize the effort required to
support RDF. Importantly, if interacting with Linked Data requires
extensive out-of-band information, it will be harder to use than media
types that does not. Secondly, it requires relevant links and that the
resulting graph can be traversed by reasonable means.

While links are abundant across the Linked Open Data (LOD) cloud, this paper will
argue that key links are missing to make it possible to traverse the
resulting graph and to enable read-write operations. Moreover, we will
argue that this shortcoming is due to that the community does not
adequately take into account the constraint known as ``Hypermedia as
the Engine of Application State'' (commonly abbreviated HATEOAS) from
the REST architectural style, see
\cite{Fielding_2000_Architectural-Styles}~Chapter~5.

@@

The second triple exists to make it possible (in the typical HTTP
case) to POST an RDF payload to some URI and the server will itself
assign a URI to the posted RDF payload.

@@

The first triple says that the current resource may be replaced by, in
the HTTP case, PUTting an RDF payload to the resource URI. The second
triple says that the resource may be deleted, typically by a HTTP
DELETE on the resource URI.

>>>>

Semantic Web services are likely to be an important source of data for
future applications, but for foreseeable future they are just one of many. A
key promise of the Semantic Web is the ability to integrate many data
sources easily. There are two key issues, first read-write operations
must be similar to how it is done with other hypermedia types, to make
it possible to use generic code to minimize the effort required to
support RDF. Importantly, if interacting with Linked Data requires
extensive out-of-band information, it will be harder to use than media
types that do not. Secondly, it requires relevant links and that the
resulting graph can be traversed by reasonable means.

While links are abundant across the Linked Open Data (LOD) cloud, this paper will
argue that key links are missing to make it possible to traverse the
resulting graph and to enable read-write operations. Moreover, we will
argue that this shortcoming is due to that the community does not
adequately take into account the constraint known as ``Hypermedia as
the Engine of Application State'' (abbreviated HATEOAS) from
the REST architectural style, see
\cite{Fielding_2000_Architectural-Styles}~Chapter~5.

@@

The second triple exists to make it possible to POST an RDF payload to
some URI and the server will itself assign a URI to the posted RDF
payload.

@@

The first triple says that the current resource may be replaced by PUTting an RDF payload to the resource URI. The second
triple says that the resource may be deleted, typically by a HTTP
DELETE on the resource URI.
